### 2013-08-29 doc/taxize_withcode_app.tex
changed to ms and appendix

\usepackage{alltt}
\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\usepackage[titletoc, title]{appendix}
\hypersetup
{
colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

@@

\begin{figure}[!h] 
\centering 
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# Fetch phylogeny from phylomatic}
phylogeny <- \hlfunctioncall{phylomatic_tree}(taxa = \hlfunctioncall{as.character}(allnames$spname), taxnames = TRUE, 
    get = \hlstring{"POST"}, informat = \hlstring{"newick"}, method = \hlstring{"phylomatic"}, storedtree = \hlstring{"R20120829"}, 
    taxaformat = \hlstring{"slashpath"}, outformat = \hlstring{"newick"}, clean = \hlstring{"true"}, parallel = TRUE)
\hlcomment{# Format teeth-labels}
phylogeny$tip.label <- \hlfunctioncall{capwords}(phylogeny$tip.label, onlyfirst = TRUE)
\hlcomment{# plot phylogeny}
\hlfunctioncall{plot}(phylogeny)
\end{alltt}
\end{kframe}

{\centering \includegraphics[width=4in]{figure/phylogeny1.pdf} 
\includegraphics[width=4in]{figure/phylogeny2.pdf}

}

@@

\caption{a phylogeny...} 
\end{figure}

@@

@@

Trait-based approaches are a promising tool in ecology. Unlike taxonomy-based methods, traits may not be constrained to biogeographic boundaries \cite{baird_toward_2011} and have potential to disentangle the effects of multiple stressors \cite{statzner_can_2010}.

To analyse trait-composition abundance data must be matched with trait databases like \cite{usseglio-polatera_biological_2000}. However these two datatables may contain species information on different taxonomic levels and perhaps data must be aggregated to a joint taxonomic level.

@@

No we can create \emph{species x sites} and \emph{traits x species} matrices, which could be plugged into methods to analyse trait responses \cite{kleyer_assessing_2012}.

@@

This is just an example how taxonomic APIs (via taxize) could be used to search for matches up- and downwards the taxonomic ladder. We are looking forward to integrate the freshwaterecology.info database \cite{freshwaterecology} into taxize, which will facilitate trait-based analyses in R.

@@

\bibliographystyle{eco_lett}
\bibliography{refs}

>>>>

\usepackage{float}
\usepackage{alltt}
\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\usepackage[titletoc, title]{appendix}
\hypersetup
{
colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

@@

% \begin{figure}[!h] 
% \centering 
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# Fetch phylogeny from phylomatic}
phylogeny <- \hlfunctioncall{phylomatic_tree}(taxa = \hlfunctioncall{as.character}(allnames$spname), taxnames = TRUE, 
    get = \hlstring{"POST"}, informat = \hlstring{"newick"}, method = \hlstring{"phylomatic"}, storedtree = \hlstring{"R20120829"}, 
    taxaformat = \hlstring{"slashpath"}, outformat = \hlstring{"newick"}, clean = \hlstring{"true"}, parallel = TRUE)
\hlcomment{# Format teeth-labels}
phylogeny$tip.label <- \hlfunctioncall{capwords}(phylogeny$tip.label, onlyfirst = TRUE)
\hlcomment{# plot phylogeny}
\hlfunctioncall{plot}(phylogeny)
\end{alltt}
\end{kframe}

\begin{figure}[h!]
\centering
\includegraphics[width=6in,height=5in]{figure/phylogeny2.pdf} 
\caption{A phylogeny}
\end{figure}

@@

% \caption{a phylogeny...} 
% \end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=7in,height=8in]{figure/map.pdf}
\caption{A phylogeny}
\end{figure}

@@

Trait-based approaches are a promising tool in ecology. Unlike taxonomy-based methods, traits may not be constrained to biogeographic boundaries [26] and have potential to disentangle the effects of multiple stressors [24].

To analyse trait-composition abundance data must be matched with trait databases like [25]. However these two datatables may contain species information on different taxonomic levels and perhaps data must be aggregated to a joint taxonomic level.

@@

Now we can create \emph{species x sites} and \emph{traits x species} matrices, which could be plugged into methods to analyse trait responses [27].

@@

This is just an example how taxonomic APIs (via taxize) could be used to search for matches up- and downwards the taxonomic ladder. We are looking forward to integrate the freshwaterecology.info database \url{www.freshwaterecology.info} into taxize, which will facilitate trait-based analyses in R.

@@

### 2013-08-29 doc/taxize_withcode_appA.Rnw
incorporated changes from karthik and naim, fixes #170, should be close to submit
changed to ms and appendix

\begin{figure}[!h] 
\centering 
<<phylogeny, eval=TRUE, dev='pdf', out.width='4in', out.height='4in', cache=TRUE, message=FALSE>>=
# Fetch phylogeny from phylomatic 
phylogeny <- phylomatic_tree(taxa=as.character(allnames$spname), taxnames=TRUE, get = 'POST', informat='newick', method = "phylomatic",
    storedtree = "R20120829", taxaformat = "slashpath", outformat = "newick", clean = "true", parallel=TRUE)
# Format teeth-labels 
phylogeny$tip.label <- capwords(phylogeny$tip.label, onlyfirst=TRUE)
# plot phylogeny 
plot(phylogeny)
@
\caption{a phylogeny...} 
\end{figure}

>>>>

% \begin{figure}[!h] 
% \centering 
<<phylogeny, eval=TRUE, dev='pdf', out.width='4in', out.height='4in', cache=TRUE, message=FALSE>>=
# Fetch phylogeny from phylomatic 
phylogeny <- phylomatic_tree(taxa=as.character(allnames$spname), taxnames=TRUE, get = 'POST', informat='newick', method = "phylomatic",
    storedtree = "R20120829", taxaformat = "slashpath", outformat = "newick", clean = "true", parallel=TRUE)
# Format teeth-labels 
phylogeny$tip.label <- capwords(phylogeny$tip.label, onlyfirst=TRUE)
# plot phylogeny 
plot(phylogeny)
@
% \caption{a phylogeny...} 
% \end{figure}

### 2013-08-29 doc/taxize_withcode_appA.tex
changed to ms and appendix

\documentclass[10pt]{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.2, 0.2, 0.2}
\newcommand{\hlnumber}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlfunctioncall}[1]{\textcolor[rgb]{0.501960784313725,0,0.329411764705882}{\textbf{#1}}}%
\newcommand{\hlstring}[1]{\textcolor[rgb]{0.6,0.6,1}{#1}}%
\newcommand{\hlkeyword}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
\newcommand{\hlargument}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
\newcommand{\hlcomment}[1]{\textcolor[rgb]{0.180392156862745,0.6,0.341176470588235}{#1}}%
\newcommand{\hlroxygencomment}[1]{\textcolor[rgb]{0.43921568627451,0.47843137254902,0.701960784313725}{#1}}%
\newcommand{\hlformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
\newcommand{\hleqformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
\newcommand{\hlassignement}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
\newcommand{\hlpackage}[1]{\textcolor[rgb]{0.588235294117647,0.709803921568627,0.145098039215686}{#1}}%
\newcommand{\hlslot}[1]{\textit{#1}}%
\newcommand{\hlsymbol}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlprompt}[1]{\textcolor[rgb]{0.2,0.2,0.2}{#1}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}

% amsmath package, useful for mathematical formulas
\usepackage{amsmath}
% amssymb package, useful for mathematical symbols
\usepackage{amssymb}

% graphicx package, useful for including eps and pdf graphics
% include graphics with the command \includegraphics
\usepackage{graphicx}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}
\usepackage{color}

% Use doublespacing - comment out for single spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\topmargin 0.0cm
\oddsidemargin 0.5cm
\evensidemargin 0.5cm
\textwidth 16cm 
\textheight 21cm

% Bold the 'Figure #' in the caption and separate it with a period
% Captions will be left justified
\usepackage[labelfont=bf,labelsep=period,justification=raggedright]{caption}

% Use the PLoS provided bibtex style
\bibliographystyle{plos2009}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

\pagestyle{myheadings}
%% ** EDIT HERE **
%% ** EDIT HERE **
%% PLEASE INCLUDE ALL MACROS BELOW
\usepackage{hyperref}
\usepackage{array}
%% END MACROS SECTION
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

\begin{document}

@@

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Calling http://taxosaurus.org/retrieve/7763b460ecdf76eee52f78e9569e7c91}}\begin{alltt}

@@

\begin{figure}[!h] 
\centering 
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# Fetch phylogeny from phylomatic}
phylogeny <- \hlfunctioncall{phylomatic_tree}(taxa = \hlfunctioncall{as.character}(allnames$spname), taxnames = TRUE, 
    get = \hlstring{"POST"}, informat = \hlstring{"newick"}, method = \hlstring{"phylomatic"}, storedtree = \hlstring{"R20120829"}, 
    taxaformat = \hlstring{"slashpath"}, outformat = \hlstring{"newick"}, clean = \hlstring{"true"}, parallel = TRUE)
\end{alltt}

@@

\end{document}

>>>>

@@

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Calling http://taxosaurus.org/retrieve/bfbc273486fa308454b9f3afaabdb3e3}}\begin{alltt}

@@

% \begin{figure}[!h] 
% \centering 
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# Fetch phylogeny from phylomatic}
phylogeny <- \hlfunctioncall{phylomatic_tree}(taxa = \hlfunctioncall{as.character}(allnames$spname), taxnames = TRUE, 
    get = \hlstring{"POST"}, informat = \hlstring{"newick"}, method = \hlstring{"phylomatic"}, storedtree = \hlstring{"R20120829"}, 
    taxaformat = \hlstring{"slashpath"}, outformat = \hlstring{"newick"}, clean = \hlstring{"true"}, parallel = TRUE)
\end{alltt}

@@
